A Domain Specific Language for SpectreGuard

### 2020-12-08 paper/main.tex
Starting an attempt at pseudocode for the information flow analysis

>>>>

\begin{figure}
\begin{lstlisting}[language=Haskell]
analyze(forest, scope, return x) = forest
analyze(forest, scope, (do { n <- allocPublic @ty size; r n })) = do
  scope.insert(Public, n)
  analyze(forest, scope, r(n))

analyze(forest, scope, (do { n <- allocSecret @ty size; r n })) = do
  scope.insert(Secret, n)
  analyze(forest, scope, r(n))

analyze(forest, scope, (do { n <- decl x; r n })) = do
  scope.insert(Public, n)
  analyze(forest, scope, r(n))

analyze(forest, scope, (do { x .= y; r })) = do
  let lhsNames = collectExprNames(x)
  let rhsNames = collectExprNames(y)

  foreach rhsName in rhsNames
    if (rhsName is secret)
      forest.addChildrenTo(rhsName, lhsNames)
    end
  end

  foreach lhsName in lhsNames
    let scopeFrame = scope.getScopeFrameOf(lhsName)

    if scope.notCurrentScopeFrame(scopeFrame)
      forest.addChildrenTo(lhsName, scopeFrame.secretVariables)
    end
  end

  analyze(forest, scope, r)

analyze(forest, scope, (do { ifThenElse cond t f; r })) = do
  let secretNames = filter(isSecretName, collectExprNames(cond))

  let tForest = copy(forest)
  let fForest = copy(forest)
  let tScope = copy(scope)
  let fScope = copy(scope)

  analyze(tForest, tScope.pushFrame(secretNames), r)
  analyze(fForest, fScope.pushFrame(secretNames), r)

  forest = union(tForest, fForest)
  analyze(forest, scope, r)
\end{lstlisting}
\caption{Information leak analysis pseudocode}
\end{figure}
